Intercoder ICBEdataset_figure_semantic_embeddings

### 2022-02-02 replication_paper/rmd/ICBEdataset_figure_semantic_embeddings.Rmd
sentences_embeddings save

```{r, messages=F, results='hide'}
library(reticulate)
#py_discover_config()

use_python("/home/skynet3/anaconda3/bin/python/")

@@

fromscratch=True

@@

@@

sentences_embeddings <- py$sentences_embeddings
dim(sentences_embeddings)

#devtools::install_github("ropenscilabs/umapr")
library(umapr)
embedding <- umap(sentences_embeddings  )

@@

codings_wide_agreed <- readRDS(paste0(here::here(), '/replication_paper/data/in/codings_wide_agreed.Rds'))
codings_wide_agreed_embeded <- codings_wide_agreed %>% ungroup() %>% left_join(sentences_embeded)

@@

@@

value_means <- codings_long_agreed_embeded %>%
      dplyr::filter(variable_normalized %in% var_keep) %>% 
      dplyr::mutate(variable_normalized=variable_normalized %>% as.factor()) %>%
      dplyr::mutate(value_normalized=value_normalized %>% as.factor()) %>%
      dplyr::select(variable_normalized,value_normalized,UMAP1,UMAP2) %>%
      group_by(variable_normalized, value_normalized) %>% 
      summarise_all(median) %>%
      group_by(variable_normalized) %>%
          mutate(variable_normalized_count=  min(n(),4)  ) %>%
      ungroup()

@@

library(RColorBrewer)
brewer_pal_info_df <- brewer.pal.info %>% add_rownames( var = "rowname") %>% arrange()
brewer_list <- list() 
for(i in c(11, 1:nrow(brewer_pal_info_df))){
  brewer_list[[as.character(i)]] <- brewer.pal(n=brewer_pal_info_df$maxcolors[i], brewer_pal_info_df$rowname[i])
}
posible_colors <- unlist(brewer_list) %>% unique(brewer_list) #%>% sample()

@@

p_semantic_embeddings <-
      codings_long_agreed_embeded_subset %>%
      ggplot(aes(x=UMAP1,y=UMAP2, color=value_normalized )) +
        geom_point(size=0.5, alpha=0.5) + 
        geom_text(data=sampled, aes(x=UMAP1, y=UMAP2, label=crisno_sent), color='black',size=1.5) +

>>>>

```{r, messages=F, results='hide'}
library(reticulate)
py_discover_config()

#use_python("/home/skynet3/anaconda3/bin/python/")
use_python("/home/tlscherer/anaconda3/bin/python")

@@

fromscratch=False

@@

```{r}
fromscratch = FALSE

if(fromscratch){
  sentences_embeddings <- py$sentences_embeddings
  dim(sentences_embeddings)
  sentences_embeddings %>% saveRDS(paste0(here::here(), '/replication_paper/data/temp/sentences_embeddings.Rds'))
}else{
  sentences_embeddings <- readRDS(paste0(here::here(), '/replication_paper/data/temp/sentences_embeddings.Rds'))
  dim(sentences_embeddings)
}

@@

#devtools::install_github("ropenscilabs/umapr")
library(umapr)
embedding <- umap(sentences_embedding)

@@

codings_wide_agreed <- readRDS(paste0(here::here(), '/replication_paper/data/in/codings_wide_agreed.Rds'))
codings_wide_agreed_embeded <- codings_wide_agreed %>% dplyr::ungroup() %>% dplyr::left_join(sentences_embeded)

@@

```{r}
# codings_long_agreed_embeded <- readRDS(paste0(here::here(), '/replication_paper/data/temp/codings_long_agreed_embeded.Rds'))
# codings_wide_agreed_embeded <- readRDS(paste0(here::here(), '/replication_paper/data/temp/codings_wide_agreed_embeded.Rds'))

@@

value_means <- codings_long_agreed_embeded %>%
      dplyr::filter(variable_normalized %in% var_keep) %>% 
      dplyr::mutate(variable_normalized=variable_normalized %>% as.factor()) %>%
      dplyr::mutate(value_normalized=value_normalized %>% as.factor()) %>%
      dplyr::select(variable_normalized,value_normalized,UMAP1,UMAP2) %>%
      dplyr::group_by(variable_normalized, value_normalized) %>% 
      dplyr::summarise_all(median) %>%
      dplyr::group_by(variable_normalized) %>%
          dplyr::mutate(variable_normalized_count=  min(dplyr::n(),4)  ) %>%
      dplyr::ungroup()

@@

library(RColorBrewer)
brewer_pal_info_df <- brewer.pal.info %>% dplyr::add_rownames( var = "rowname") %>% dplyr::arrange()
brewer_list <- list() 
for(i in c(11, 1:nrow(brewer_pal_info_df))){
  brewer_list[[as.character(i)]] <- brewer.pal(n=brewer_pal_info_df$maxcolors[i], brewer_pal_info_df$rowname[i])
}
posible_colors <- unlist(brewer_list) %>% unique(brewer_list) #%>% sample()

@@

library(ggplot2)
p_semantic_embeddings <-
      codings_long_agreed_embeded_subset %>%
      ggplot(aes(x=UMAP1,y=UMAP2, color=value_normalized )) +
        geom_point(size=0.5, alpha=0.5) + 
        geom_text(data=sampled, aes(x=UMAP1, y=UMAP2, label=crisno_sent), color='black',size=1.5) +
